\documentclass[conference]{IEEEtran}
\usepackage[english]{babel}
\usepackage{cite,setspace}
\usepackage[autostyle]{csquotes}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\graphicspath{{images/}}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage[outputdir=output]{minted}
%\usemintedstyle{autumn} % friendly, colorful
%\newminted{c}{mathescape, linenos, numbersep=5pt, gobble=0, frame=lines, framesep=2mm}
%\definecolor{background}{gray}{0.90}
%\newminted{bash}{bgcolor=background}
%\newminted{console}{bgcolor=background}
%\usemintedstyle[console]{bw}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{CS5800 Proposal}

\author{\IEEEauthorblockN{Mark Wesley Harris}
Dr. Sudhanshu Semwal, CS 5800\\
University of Colorado at\\
Colorado Springs\\\\
Fall, 2019}

\maketitle

\begin{abstract}
\end{abstract}

\section{Introduction}
\label{sec:introduction}

\begin{thebibliography}{15}
\bibitem{ref:bessel_functions} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{ref:predictive_rendering} Alexander Wilkie, Andrea Weidlich, Marcus Magnor, and Alan Chalmers. 2009. ``Predictive Rendering.'' In ACM SIGGRAPH ASIA 2009 Courses (SIGGRAPH ASIA '09). ACM, New York, NY, USA, Article 12, 428 pages.
\bibitem{ref:frame_prediction} R. Mahjourian, M. Wicke and A. Angelova, ``Geometry-Based Next Frame Prediction From Monocular Video''. 2017 IEEE Intelligent Vehicles Symposium (IV), Los Angeles, CA, 2017, pp. 1700-1707.
\bibitem{ref:image_captioning} Oriol Vinyals, Alexander Toshev, Samy Bengio, and Dumitru Erhan. 2017. ``Show and Tell: Lessons Learned from the 2015 MSCOCO Image Captioning Challenge.'' IEEE Trans. Pattern Anal. Mach. Intell. 39, 4 (April 2017), 652-663.
\bibitem{ref:posecnn} Yu Xiang, Tanner Schmidt, Venkatraman Narayanan, Dieter Fox. ``PoseCNN: A Convolutional Neural Network for 6D Object Pose Estimation in Cluttered Scenes.'' CoRR abs/1711.00199 (2018): n. pag.
\bibitem{ref:pixelcnn_decoders} A\"{a}ron van den Oord, Nal Kalchbrenner, Oriol Vinyals, Lasse Espeholt, Alex Graves, and Koray Kavukcuoglu. 2016. ``Conditional Image Generation With PixelCNN Decoders.'' In Proceedings of the 30th International Conference on Neural Information Processing Systems (NIPS'16), Daniel D. Lee, Ulrike von Luxburg, Roman Garnett, Masashi Sugiyama, and Isabelle Guyon (Eds.). Curran Associates Inc., USA, 4797-4805.
\bibitem{ref:pixelcnn++} Time Salimans, Andrej Karpathy, Xi Chen, Diederik P. Kingma. 2017. ``PixelCNN++: Improving The PixelCNN with Discretized Logistic Mixture Likelihood and Other Modifications.'' ICLR Conference Paper (2017).
\bibitem{ref:multi_source} Eunvyung Park, Xufeng Han, Tamara L. Berg, Alexander C. Berg. ``Combining Multiple Sources of Knowledge In Deep CNN's For Action Recognition.'' 2016 IEEE Winter Conference on Applications of Computer Vision (WACV) (2016): 1-8.
\bibitem{ref:pose_guided} Liquian Ma, Xu Jia, Qianru Sun, Bernt Schiele, Tinne Tuytelaars, Luc Van Gool. ``Pose Guided Person Image Generation.'' NIPS (2017).
\bibitem{ref:multi_view} Bo Zhao, Xiao Wu, Zhi-Qi Cheng, Hao Liu, Zequn Jie, and Jiashi Feng. 2018. ``Multi-View Image Generation from a Single-View.'' In Proceedings of the 26th ACM international conference on Multimedia (MM '18). ACM, New York, NY, USA, 383-391.
\bibitem{ref:info_gan} Xi Chen, Yan Duan, Rein Houthooft, John Schulman, Ilya Sutskever, Pieter Abbeel. ``InfoGAN: Interpretable Representation Learning by Information Maximizing Generative Adversarial Nets.'' NIPS (2016).
\bibitem{ref:spatiotemporal} Christoph Schied, Anton Kaplanyan, Chris Wyman, Anjul Patney, Chakravarty R. Alla Chaitanya, John Burgess, Shiqiu Liu, Carsten Dachsbacher, Aaron Lefohn, and Marco Salvi. 2017. Spatiotemporal variance-guided filtering: real-time reconstruction for path-traced global illumination. In Proceedings of High Performance Graphics (HPG '17). ACM, New York, NY, USA, Article 2, 12 pages.
\bibitem{ref:monsters} Dean Takahashi, ``How Pixar made Monsters University, its
latest technological marvel''. April 24, 2013. Article.
\bibitem{ref:pix2pix} Phillip Isola, ``Pix2Pix''. April 21, 2019. Github
(phillipi/pix2pix)
\bibitem{ref:pix2pix_deblur} CeShine Lee, ``Pix2Pix Deblur''. September 17, 2017. GitHub
(ceshine/pix2pix-deblur).
\end{thebibliography}

%==========================================================
\end{document}
%==========================================================
